Assessing variations in the chemistry of fossil- and modern-*Pinus* pollen

### 2021-06-11 manuscript.Rmd
added woutersen to jardine paragraph

ADD COMPARISON TO JARDINE PAPERS and other (e.g. Woutersen)
Comparisons to other studies that looked at acetolysed and fossil samples show similarities between our acetolysed *Pinus* pollen and other taxa.
E.g. the carb region 1000 - 1200 in our Pine is most similar to the acetolysed extant poaceae set of @jardineSporopolleninChemistryIts2021, where two large peaks at 1040 and 1190/1170 are visible similar to our samples.

@@

### pollen chemical differences

>>>>

Comparisons to other studies that looked at acetolysed and fossil samples show similarities between our acetolysed *Pinus* pollen and other taxa.
E.g. the carb region 1000 - 1200 in our Pine is most similar to the acetolysed extant poaceae set of @jardineSporopolleninChemistryIts2021 and acetolyzed herbarium *Nitrariaceae* pollen [@woutersenNovelApproachStudy2018], where two peaks at 1040 and 1190/1170 are visible and similar to our samples.

@@

### Pollen chemical differences
